master thesis

### 2018-02-25 Paper - Latex/Paper - Skizze - v2.tex
count updates

      \begin{table} [h]
        \begin{center}
          \begin{tabular}{ |l|r|r||r|r|r| }
            \hline
            Domain / Kingdom & \# internal & \# leaf & Rootnode & \multicolumn{2}{c|}{without and with rounding} \\ 
            / Phylum / Class & \multicolumn{2}{c||}{nodes} & state & \# origins & \# losses \\
            & & & state & (FL -> P) & (P -> FL) \\
            \hline \hline
            Eukaryota & 241974 & 2293463 & 1.0 & 415 & 495 \\
            & & & P & 462 & 369 \\
            \hline \hline
            Metazoa & 179944 & 1491012 & 0.5 & 294 & 206 \\
            & & & & 321 & 129 \\ \hline
            Fungi & 9534 & 314571 & 0.5 & 80 & 263 \\
            & & & & 97 & 222 \\ \hline
            Chloroplastida & 43486 & 412434 & 0.0 & 40 & 7 \\
            & & & FL & 42 & 2 \\
            \hline \hline            
            Arthropoda & 120479 & 1198981 & 0.0 & 260 & 170 \\
            & & & FL & 281 & 108 \\ \hline
            Apicomplexa & 239 & 1863 & 1.0 & 0 & 1 \\
            & & & P & 0 & 1 \\ \hline
            Nematoda & 3437 & 30127 & 1.0 & 0 & 17 \\
            & & & P & 2 & 11 \\ \hline
            Chordata & 30761 & 91785 & 0.0 & 12 & 1 \\
            & & & FL & 12 & 1 \\ \hline
            Platyhelminthes & 4459 & 22683 & 1.0 & 0 & 5 \\
            & & & P & 0 & 5 \\ \hline
            \hline \hline            
            Insecta & 91256 & 989572 & 0.0 & 234 & 107 \\
            & & & FL & 245 & 77 \\ 
            \hline  
          \end{tabular}
        \end{center}
        \caption{Origins and losses}
        \label{table:origins and losses} 
      \end{table}

>>>>

      \begin{table} [h]
        \begin{center}
          \begin{tabular}{ |l|r|r||r|r|r| }
            \hline
            Domain / Kingdom & \# internal & \# leaf & Rootnode & \multicolumn{2}{c|}{without and with rounding} \\ 
            / Phylum / Class & \multicolumn{2}{c||}{nodes} & state & \# origins & \# losses \\
            & & & state & (FL -> P) & (P -> FL) \\
            \hline \hline
            Eukaryota & 241974 & 2293463 & 1.0 & 415 & 363 \\
            & & & P & 462 & 369 \\
            \hline \hline
            Metazoa & 179944 & 1491012 & 0.5 & 294 & 123 \\
            & & & & 321 & 129 \\ \hline
            Fungi & 9534 & 314571 & 0.5 & 80 & 222 \\
            & & & & 97 & 222 \\ \hline
            Chloroplastida & 43486 & 412434 & 0.0 & 40 & 2 \\
            & & & FL & 42 & 2 \\
            \hline \hline            
            Arthropoda & 120479 & 1198981 & 0.0 & 260 & 102 \\
            & & & FL & 281 & 108 \\ \hline
            Apicomplexa & 239 & 1863 & 1.0 & 0 & 1 \\
            & & & P & 0 & 1 \\ \hline
            Nematoda & 3437 & 30127 & 1.0 & 0 & 11 \\
            & & & P & 2 & 11 \\ \hline
            Chordata & 30761 & 91785 & 0.0 & 12 & 1 \\
            & & & FL & 12 & 1 \\ \hline
            Platyhelminthes & 4459 & 22683 & 1.0 & 0 & 5 \\
            & & & P & 0 & 5 \\ \hline
            \hline \hline            
            Insecta & 91256 & 989572 & 0.0 & 234 & 77 \\
            & & & FL & 245 & 77 \\ 
            \hline  
          \end{tabular}
        \end{center}
        \caption{Origins and losses}
        \label{table:origins and losses} 
      \end{table}
